\chapter{General Information}

\label{chap:introduction}

\section{Scope}
SHEAVY is a consitent tool to handle and manage an epidemic in an efficient way.
SHEAVY can be used worldwide working together with infrastrucutres like
gouvernements, health organisations and hospitals. This document's goal is to
provide the basic knowledge to use SHEAVY. There is no source code or
programming aspect in this file. \\

\section{Purpose}
The user manual guide was written to show how different users can acces to the
system and to understand its workflow.\\



\section{Intended audience}
EXTERIOR: All person which isn't involved with the crisis management will have a
simple guideline to access to the news published in the application.\\
\\
INTERIOR: All person activly helping controling the crisis will have a overall
view of the interface. They will know where to find which information. Our
contact list search will be explained to let them find anybody easily, person or
institution.\\

\section{SHeavy}
SHEAVY is an epidemic crisis management web based tool. Data from different
sources will be fetched together to centralize all the known statuses and
information of the crisis in some simple clicks. Its also a searchtool to find
someone involved in the crisis easily and trough a realtime view interface, it
will be fast to know how the ressources are distributed. A feature will alert
the users of an important message. It keeps also track of the locations of the
users to\\
\begin{description}
 \item[1.] Prevent them accessing an unauthorized zone
 \item[2.] Guide them with GPS to secure zones.
\end{description}

\subsection{Actors \& Functionalities}
SHeavy has different functionalities for several Actors. Here is an overview.\\

\subsubsection{Common Users}
A common user is defined as an end user who uses SHeavy only in order to
collect information about the possible epidemic and uses the given information
to avoid the infection.\\
\begin{description}
 \item[$\bullet$] Common users are the principle target of SHeavy. They are
 going to use the application in order to reach information about a possible
 or several epidemic and follow the instructions given by SHeavy. Common users will get warnings if accessing an infected
zone by gps tracking. They will have paths to follow to access and find the
safe zones.
\end{description}

\section{Creator procedures}

The Creator only has one main function which is to set in place the system to
handle an epidemical crisis. He has to make sure every actor can access it and
keep it accessible as well as maintained and updated.\\
\begin{description}
 \item[$\bullet$] Create and set up the system.
\end{description} 

\subsubsection{Chief}
The chief is a designed person to be responsable of a action group in a specific
domain e.g. Medic or Military.\\
\begin{description}
 \item[$\bullet$] Has to inform whenever he's affected to a mission, where his
 team location is.
\end{description} 

\subsubsection{Coordinators}
The Coordinator is an intermediate between all the Actors and the System. He has
several main functions such as to keep the system functional and updated.\\
\begin{description}
 \item[$\bullet$] Maintain the system operational: The Coordinator's main task
 is to keep the system operational.
 \item[$\bullet$] If necessary he will perform some improvements and bugs
 corrections on the system and also keep the system maintained and updated.
\end{description} 

\subsubsection{Medical Departement}
The Medical Departement is subdivied in two groups. The laboratory and the
Doctors. They have the duty to recognize an epidemic and send the alert
statement that enter the population in crisis. They will work together to stop
the epidemic.\\
\begin{description}
 \item[$\bullet$] Gives the alert of the beginning of an epidemic.
\end{description} 

\subsubsection{Laboratory}
The Laboratory is a medical group which goal is to find a cure to the virus. In
constant collaboration with different medical chiefs they will get relevant
information of the evolution of the epidemic in realtime. They also get the
blood samples and reports from the doctors.\\
\begin{description}
 \item[$\bullet$] Analizing the blood samples to isolate the virus and demantle
 its structure to provide an antivirus.
 \item[$\bullet$] Gives a guideline to the application as a news so that all the
 people knows how to protect itself from become infected.
\end{description} 

\subsubsection{Doctors}
Doctors are in charge of providing the antidote to the patients. They will be on
site to care of the infected people. \\
\begin{description}
 \item[$\bullet$] Write Reports that will be sent to the laboratory.
 \item[$\bullet$] Take care of the ill people the time that an antivirus is
 found.
 \item[$\bullet$] Test antiviruses and report if it's effective or not.
\end{description} 

\subsubsection{Government Departement}
The Government Departement is divided into two divisions. Both Central
Headquarter and Military Departement are working together in order to create an harmonious teamwork 
flow with the other authorities and finally achieve a common aim.\\

\subsubsection{Central Headquarter}
The Central Headquarter is the intermediate between the internal authorities and
external governments. They are the main actors who allow SHeavy to work world
wide.\\
\begin{description} 
 \item[$\bullet$] Create the communication with all Government world wide in
 order to merge all authorities together. This merge consists to unify medical
 departements in order to find a cure or to stop the epidemic rapidly.\\
 \item[$\bullet$] Manage available ressources in order to create intervention
 groups.\\ 
\end{description} 

\subsubsection{Military Departement}
The Military Departement are responsible for the security of all zones and also
to reduce the panic for organisational and colaborational purposes. They
represent the strength of the Government.\\
\begin{description} 
 \item[$\bullet$]They are responsible for the security of all zones.
 \item[$\bullet$]In order to avoid riot they have to make sure that everyone are
 colaborative. 
 \item[$\bullet$]Execute checks in several aeroports in order to avoid the
 spreading out of the epidemic.
\end{description}  

\subsection{Operating environment}
SHEAVY is a webbased application. It has a server and a client side. The server
needs to be powerfull to handle the mass of information. Clients need to have a
good internet access and a basic system requirement to access fast their
pages.\\

\subsubsection{System requirements: Client}
\begin{tabular}{|c|c|}
\hline
\multicolumn{2}{|c|}{\textbf{Phone Application}} \\
\hline
\multicolumn{2}{|c|}{\textit{\textbf{Android}}} \\
\hline
OS & Android \\
\hline
Hardware & ARM 5 Dual Core \\
\hline
\multicolumn{2}{|c|}{\textit{\textbf{iOS}}} \\
\hline
Operating System & iOS 8 \\
\hline
Hardware & iPhone 5 \\
\hline
\end{tabular}

\subsubsection{System requirements: Server}
\begin{tabular}{|c|c|}
\hline
\multicolumn{2}{|c|}{\textbf{Server Application}} \\
\hline
\multicolumn{2}{|c|}{\textit{\textbf{Linux x86/x64}}} \\
\hline
Kernel & 4.8.1 \\
\hline
Hard disk space & 10 TB   \\
\hline
Processeur & Intel Xeon E7-8893 \\
\hline
RAM & 32 GB \\
\hline
\end{tabular}

\section{Document structure}  
Information on how this document is organised and it is expected to be
used. Recommendations on which members of the audience
should consult which sections of the document, and explanations about the used
notation (i.e. description of formats and conventions) must also be provided.\\








