\chapter{Product information}
%Reducing the spacing from the title
\vspace{-6em}

\section{Identification}
SHeavy\textregistered is a web based software developed by CrisYs Corp. whose goal is to
prevent the spreading of epidemics but also to manage differents oragnizations to handle epidemics
in real time.

\section{Copyright}
A copyright is an exclusive right granted to an author of a literary, musical,
audiovisual or artistic work, giving the author the sole right to reproduce and distribute that work. 
There are several different types of copyrights which are associated with CrisYs
Corp products. These include various copyrights in CrisYs Corp's
software source code, executable code, product packaging, hardware and publications.

\section{Trademark notices}
Trademarks are the distinctive names, words, logos, designs and symbols used to distinguish our
products or company. Some of our recognized trademarks include CrisYs
Corp\textregistered, SHeavy\textregistered. The CrisYs Corp\textregistered trademark has been filed
in many countries throughout the world and registrations have been issued in
CrisYs Corp's name in many countries. 

\section{Restrictions}
There are no restrictions on copying or distributing the
software's associated documentation but the distribution of the software is only
allowed over the buyer's network.

\section{Warranties}
SHeavy warrants for an entire lifetime following delivery of the Software that
the Software will perform substantially in accordance with the user manual.
Additionally SHeavy warrants also that our support is available 24h/24h and
7/7 days.

\section{Contractual obligations}
Having a function ready system. Maintain the web application deployed for each
actor.

\section{Disclaimers}
SHeavy only shares instructions from trustful organizations and in no event
will SHeavy or its distributors and their dealers be liable to you for any
damages and any losts or incidental or consequential damage.

\section{Contact}

\subsection{Online assistance}
Visit the CrisYs Corp to get quick answers to your question or refer to our
online support at \url{https://www.crisyscorp.com/support}. You can also get
help and advices by contacting us on \url{https://www.crisyscorp.com/chat} or by
\href{mailto:contact@crisyscorp.com}{contact@crisyscorp.com}.

\subsection{Telephone assistance}
When you contact our support by telephone make sure that your problem is not already
described on \url{https://www.crisyscorp.com/support}. Otherwise choose one of
our callcenters.\\
CSC 1:  4884224179-85 \\
CSC 2:  4884224179-86 \\ 
More callcenters are available at \url{https://www.crisyscorp.com/callcenter}.\\

